---
title: "Input Data"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Input Data}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

## Overview

```{r, include = FALSE}
knitr::opts_chunk$set(collapse = TRUE)
```

The MASTA algorithm is a semi-supervised learning method and it requires three input data files.

- A long form longitudinal data for predicting the time-to-event outcomes [`longitudinal`]

- A follow up time data to inform the length of follow-up time for each patient [`follow_up_time`]

- A labeled data with time-to-event outcomes and baseline predictors [`survival`]

In Step I of the MASTA algorithm, `longitudinal` and `follow_up_time` will be used  to extract features from estimated subject-specific intensity functions of individual encounters. In Step II of the MASTA algorithm, `survival` and `follow_up_time` will be used to train and evaluate risk prediction models with survival outcomes.
The `MASTA` package contains these three data files as a sample.


```{r, echo=FALSE, fig.width=5, fig.height=3}
DiagrammeR::grViz("
digraph flowchart {
  node [fontname = Helvetica, shape = rectangle]        
  tab1 [label = '@@1']
  tab2 [label = '@@2']
  tab3 [label = '@@3']
  tab4 [label = '@@4']
  tab5 [label = '@@5']
  tab1 -> tab2;
  tab1 -> tab3;
  tab2 -> tab4;
  tab2 -> tab5;
}
[1]: 'Input Data'
[2]: 'Labeled (n = 1,100)'
[3]: 'Unlabeled (N = 20,000)'
[4]: 'Training (600)'
[5]: 'Validation (500)'
")
```


```{r, eval=FALSE}
library(MASTA)
```

## Longitudinal Encounter Data
```{r, eval=FALSE}
?longitudinal
```

```{r}
head(longitudinal)
table(longitudinal$code)
```

## Follow-up Time Data with the training/validation indicator
One subject has one record in this data. The variable `train_valid` indicates which cohort each subject belong to, training (1) or validation (2).  
```{r, eval=FALSE}
?follow_up_time
```

```{r}
head(follow_up_time)
```

## Time-to-Event Data
One subject has one record in this data. The variable `event_ind` indicates whether the subject has an event (1) or not (0). For those who do not have event (i.e., `event_ind=0`), `event_time` in this data set should be the same as the `fu_time` in follow_up_time.
The current version of the MASTA package requires that at least one baseline predictor is included in this data.   

```{r, eval=FALSE}
?survival
```

```{r}
head(survival)
```
