---
title: "MASTA"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{MASTA}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

## Overview

The MASTA algorithm is a semi-supervised learning method.
The implementation has 2 steps. 
In Step I, `longitudinal` and `follow_up_time` will be used to extract features from estimated subject-specific intensity functions of individual encounters. 
In Step II, `survival` and `follow_up_time` will be used to train and evaluate risk prediction models with survival outcomes.

For the details of the data preparation, please see the vignette for it. 

## Installation

Load the package into R.

```{r, echo=FALSE}
library(MASTA)
```

## Data Example

```{r}
head(longitudinal)
table(longitudinal$code)

head(follow_up_time) ; 
nrow(follow_up_time) ;

head(survival)
nrow(survival)
```

## Run Step I (feature selections)
```{r}
ptm = proc.time()
Z <- fpca.combine(longitudinal, follow_up_time, K.select = "PropVar")
print(proc.time() - ptm)
```

## Run Step II (fitting)
Using the object drived from `fpca.combine` and the two data files (`survival'
```{r}
ptm = proc.time()
b <- masta.fit(Z, survival, follow_up_time, Tend=1, cov_group = NULL, thresh = 0.7, PCAthresh = 0.9, seed = 100)
b
print(proc.time() - ptm)
```

